---
title: "Modificación Datos"
output:
  html_document:
    df_print: paged
---

```{r}
setwd("~/Documents/GitHub/tfg/Datos y formulas")
source("Rfunctions.R")
# Load the data
tfg <- read.csv("stackoverflow_full.csv")
# Recall main properties
str(tfg)
library(dplyr)
```

```{r}
#Check for missing values 
missing_values <- colSums(is.na(tfg))
print(missing_values)
```

```{r}
#Crear nuevas columnas 
top_skills <- list(
  SQL = c("SQL", "sql", "$SQL", "\\b\\w*SQL\\b"),
  python = c("python", "Python", "py"),
  java = c("javascript", "Java", "\\b\\w*Java\\b"),
  c_plus_plus =  c("c++", "C++", "\\b\\w*C\\b"),
  cloud = c("\\b\\w*Cloud\\b", "AWS", "Cloud Services", "Azure", "Google Cloud Platform", "Oracle", "IBM")
)

# Function to check if any of the skill words are present in the text
check_skill <- function(text, skill_words) {
  any(sapply(skill_words, function(skill_word) grepl(paste0("\\b", gsub("\\+", "\\\\+", skill_word), "\\b"), tolower(text), ignore.case = TRUE)))
}

# Loop through each candidate row
for (i in 1:nrow(tfg)) {
  # Initialize new columns for each skill
  for (skill_name in names(top_skills)) {
    tfg[i, skill_name] <- as.integer(check_skill(tfg[i, "HaveWorkedWith"], top_skills[[skill_name]]))
  }
}

top_skillslist <- c("SQL","python", "java", "c_plus_plus", "cloud")
topskills_list <- tfg %>% select(all_of(top_skillslist))

tfg$SQL <- as.factor(tfg$SQL)
tfg$python <- as.factor(tfg$python)
tfg$java <- as.factor(tfg$java)
tfg$c_plus_plus <- as.factor(tfg$c_plus_plus)
tfg$cloud <- as.factor(tfg$cloud)
```

```{r}
#convertir pais en continente
unique_countries <- unique(tfg$Country)
unique_countries

# Check for unique values in the 'Country' column
unique_countries <- unique(tfg$Country)

# Define a function to segment countries into continents
segment_country <- function(country) {
   if (country %in% c("United States of America", "Canada", "Mexico")) {
    return("NorthAmerica")
  } else if (country %in% c("United Kingdom of Great Britain and Northern Ireland", "France", "Germany", "Spain", "Italy", "Portugal", "Belgium", "Netherlands", "Austria", "Switzerland", "Denmark", "Ireland", "Norway", "Sweden", "Finland", "Greece", "Czech Republic", "Slovakia", "Hungary", "Poland", "Russian Federation")) {
    return("Europe")
  } else if (country %in% c("Brazil", "Argentina", "Chile", "Colombia", "Peru", "Venezuela, Bolivarian Republic of...", "Bolivia", "Ecuador", "Guyana", "Paraguay", "Suriname", "Uruguay")) {
    return("SouthAmerica")
  } else if (country %in% c("China", "Japan", "South Korea", "Viet Nam", "India", "Sri Lanka", "Pakistan", "Bangladesh", "Indonesia", "Malaysia", "Philippines", "Taiwan", "Thailand", "Cambodia", "Myanmar", "Laos", "Singapore", "Hong Kong (S.A.R.)", "Afghanistan", "Bahrain", "Iran, Islamic Republic of...", "Iraq", "Israel", "Jordan", "Kazakhstan", "Kuwait", "Kyrgyzstan", "Lao People's Democratic Republic", "Lebanon", "Maldives", "Mongolia", "Nepal", "North Korea", "Oman", "Qatar", "Saudi Arabia", "Syria", "Tajikistan", "Timor-Leste", "Turkey", "Turkmenistan", "United Arab Emirates", "Uzbekistan", "Yemen")) {
    return("Asia")
  } else if (country %in% c("Australia", "New Zealand", "Fiji", "Papua New Guinea", "Solomon Islands", "Vanuatu", "Samoa", "Tonga", "Kiribati", "Marshall Islands", "Micronesia, Federated States of", "Nauru", "Palau", "Tuvalu")) {
    return("Oceania")
  } else if (country %in% c("Egypt", "South Africa", "Nigeria", "Algeria", "Morocco", "Kenya", "Ghana", "Angola", "Sudan", "Tunisia", "Mauritius", "Mauritania", "Seychelles", "Cape Verde", "Madagascar", "Botswana", "Zambia", "Zimbabwe", "Uganda", "Malawi", "Namibia", "Lesotho", "Liberia", "Sierra Leone", "Mali", "Guinea", "Senegal", "Gambia", "Benin", "Burkina Faso", "Togo", "Ivory Coast", "Gabon", "Cameroon", "Niger", "Chad", "Central African Republic", "Somalia", "Ethiopia", "Djibouti", "Eritrea", "Mozambique", "Comoros", "Rwanda", "Burundi", "Tanzania", "Congo, Republic of the...", "Democratic Republic of the Congo", "Equatorial Guinea", "Sao Tome and Principe", "Cabo Verde", "Sierra Leone", "Grenada", "Barbados", "Jamaica", "Haiti", "Cuba", "Dominican Republic", "Haiti", "Trinidad and Tobago", "Bahamas", "Antigua and Barbuda", "Saint Lucia", "Saint Vincent and the Grenadines", "Grenada", "Dominica", "Saint Kitts and Nevis", "Guyana", "Suriname", "French Guiana")){
    return("Africa")
  } else {
    return("Other")
  }
}
# Create a new column 'Continent'
tfg$Continent <- sapply(tfg$Country, segment_country)
```

```{r}
# Obtener el conteo de los continentes
continent_counts <- table(tfg$Continent)

# Crear un data frame con los datos
continent_data <- data.frame(Continent = names(continent_counts),
                             Count = as.vector(continent_counts))

# Crear el pie chart con ggplot2
pie_chart <- ggplot(continent_data, aes(x = "", y = Count, fill = Continent)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  theme_void() +
  geom_text(aes(label = paste0(round(Count/sum(Count) * 100, 1), "%")), position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = c('skyblue', 'lightcoral', 'lightgreen', 'lightgray', 'lightpink', 'lightyellow','violet')) +
  ggtitle("Distribution of Countries by Continent") +
  theme(plot.title = element_text(hjust = 0.5))

# Mostrar el pie chart
print(pie_chart)
```

```{r}
#proporcion de datos en genero
# numero de genero 
gender_counts <- table(tfg$Gender)

# Crear un data frame con los datos
gender_data <- data.frame(Gender = names(gender_counts),
                             Count = as.vector(gender_counts))
pie_chart_gender <- ggplot(gender_data, aes(x = "", y = Count, fill = Gender)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  theme_void() +
  geom_text(aes(label = paste0(round(Count/sum(Count) * 100, 1), "%")), position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = c('skyblue', 'lightcoral', 'lightgreen')) +
  ggtitle("Distribution of Gender") +
  theme(plot.title = element_text(hjust = 0.5))

print(pie_chart_gender)
```

```{r}
tfg <- subset(tfg, tfg$Gender != "NonBinary")
tfg$Gender <- as.factor(tfg$Gender)
levels(tfg$Gender)
```

```{r}
#datatypes
for (col in names(tfg)) {
  if (is.character(tfg[[col]])) {
    tfg[[col]] <- as.factor(tfg[[col]])
  }
}

tfg$Employment <- as.factor(tfg$Employment)
tfg$Employed <- as.factor(tfg$Employed)
tfg$HaveWorkedWith <- as.character(tfg$HaveWorkedWith)

str(tfg)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
